Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec2-review-of-graph-neural-network.tex
更新response.
更新sample size对accuracy的影响.

Different from the full-batch inference, the sample-based inference only predicts labels for part of vertices/edges each time, limiting the GPU memory usage during inference.
%
It first samples a subgraph related to inference from the input graph and then performs the full-batch inference on the sampled subgraph.
%
The sampling method depends on the prediction task.
%
Taking the node classification scenario as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
%
Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
%
The sample-based inference is suitable for processing big graphs.
%
It stores the whole input graph and its feature vectors in the main memory.
%
It processes the whole graph in batches.
%
The subgraph of each batch is sampled on the CPU side and sent to the GPU side to perform inference.
%
By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.

>>>>

Different from the full-batch inference, the sample-based inference only predicts labels for part of vertices/edges each time, limiting the GPU memory usage during inference.
%
It first samples a subgraph related to inference from the input graph and then performs the full-batch inference on the sampled subgraph.
%
The sampling method depends on the prediction task.
%
Taking the node classification scenario as an example, if there are $L$ GNN layers in the GNN, the hidden vector outputted by the last GNN layer of each vertex $\MyVec{h}^L_x$ is only related to the $L$-hop neighborhood of $v_x$.
%
Thus, if we want to predict labels for a group of vertices, we only need to sample a subgraph that contains $L$-hop neighborhoods of all given vertices.
%
The sample-based inference is suitable for processing big graphs.
%
It stores the whole input graph and its feature vectors in the main memory.
%
It processes the whole graph in batches.
%
The subgraph of each batch is sampled on the CPU side and sent to the GPU side to perform inference.
%
By using small batch sizes, the peak memory usage during inference can be limited under the GPU memory capacity.
%
The sample-based inference is also suitable for the online inference scenario that the topology of the graph evolves over time.
%
When a graph update arrives, the subgraph affected by the update is sampled and inferences are only performed on the sampled subgraph.it. that are affected by , avoiding conducting repeated inferences for the whole graph.

### 2020-12-23 NEUROC/sec3-experiment-design.tex
更新sample size对accuracy的影响.

    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training? Does the use of sampling techniques in training affect the test accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training/inference of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The test accuracy of GNNs may also be affected.
          %
          To validate effectiveness of sampling techniques, we measured the training time, peak memory usage and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they will be the keys to conduct GNN training on very big graphs.
          %
          If they are not effective, we want to find out which impairs its efficiency.
          %

>>>>

    \item[Q4] \emph{Can sampling techniques remove performance bottlenecks in GNN training? Does the use of sampling techniques in training affect the model accuracy?} (Section~\ref{sec:effects_of_sampling_techniques_on_performance})

          Theoretically, sampling techniques can significantly reduce the number of graph neurons that participate in the training of a batch.
          %
          Consequently, the processing time and memory usage per batch should also decrease.
          %
          The model accuracy of GNNs may also be affected.
          %
          To validate effectiveness of sampling techniques, we measured the training time, peak memory usage and test accuracy under different batch sizes.
          %
          If sampling techniques are effective, they will be the keys to conduct GNN training on very big graphs.
          %
          If they are not effective, we want to find out which impairs its efficiency.
          %
